%\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
%
%% moderncv themes
%\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
%\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page
%
%% character encoding
%%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean
%
%% adjust the page margins
%\usepackage[scale=0.75]{geometry}
%%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...
%
%% personal data
%\name{John}{Doe}
%\title{Resumé title}                               % optional, remove / comment the line if not wanted
%\address{street and number}{postcode city}{country}% optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
%\phone[mobile]{+1~(234)~567~890}                   % optional, remove / comment the line if not wanted; the optional "type" of the phone can be "mobile" (default), "fixed" or "fax"
%\phone[fixed]{+2~(345)~678~901}
%\phone[fax]{+3~(456)~789~012}
%\email{john@doe.org}                               % optional, remove / comment the line if not wanted
%\homepage{www.johndoe.com}                         % optional, remove / comment the line if not wanted
%\social[linkedin]{john.doe}                        % optional, remove / comment the line if not wanted
%\social[twitter]{jdoe}                             % optional, remove / comment the line if not wanted
%\social[github]{jdoe}                              % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted
%
%% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%%\makeatletter
%%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%%\makeatother
%%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS
%
%% bibliography with mutiple entries
%%\usepackage{multibib}
%%\newcites{book,misc}{{Books},{Others}}
%%----------------------------------------------------------------------------------
%%            content
%%----------------------------------------------------------------------------------
\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage[utf8]{inputenc}
\usepackage{ae,aecompl}
\usepackage{lmodern}
\renewcommand*\familydefault{\sfdefault}
\usepackage[main=ngerman,english]{babel}
\usepackage[T1]{fontenc}
\usepackage{parskip}
\usepackage{verbatim}
\usepackage{microtype}
\usepackage{abbrevs}
\usepackage{xspace}
\usepackage{graphicx}

% change \emaillink so it doesn't make a link by default
\renewcommand*{\emaillink}[2][]{%
	\ifthenelse{\equal{#1}{}}%
	{#2}%
	{\href{mailto:#2}{#1}}}

%%---hyperref options---
%\AfterPreamble{\hypersetup{
%	colorlinks=false,
%	urlbordercolor=color2,
%	
%}}


%%---- Design ----
%
\moderncvstyle{classic}
%\moderncvcolor{blue}

\renewcommand*{\addressfont}{\mdseries}

\definecolor{color0}{cmyk}{0,0,0,1.00}% black
\definecolor{color1}{HTML}{009ee0}% MPI CEC Blau
\definecolor{color2}{cmyk}{0.0,0.0,0,0.85}% grau

\usepackage[left=2.5cm,right=2cm,top=2cm,bottom=2cm]{geometry}
%\usepackage[scale=0.8]{geometry}

%---- Persönliche Daten ----

\name{Benedikt M.}{Flöser}
%\address{Wallstraße 10-12}{45468 Mülheim a.d. Ruhr}
%\phone{+49\,(0)208\,74174060}
%\mobile{+49\,(0)174\,4013271}
\email{bfloeser@posteo.de}
\extrainfo{* September 1989}
%\photo[3cm][0pt]{../../../Bilder/Bewerbungsfotos_FlorianGutzeit/quer_ausschnitt3_dunkel_l}
%\photo[3cm][0pt]{../../../Bilder/Bewerbungsfotos_FlorianGutzeit/hoch_hell_l}

\title{Dr. rer. nat.}
\author{Benedikt M. Flöser}

%---- Strichdicke -----
\renewcommand{\section}[1]{\vspace{2.5ex}%
  \phantomsection{}% reset the anchor for hyperrefs
  \addcontentsline{toc}{part}{#1}%
  \parbox[m]{\hintscolumnwidth}{\raggedleft\hintfont{\color{color1}\rule{\hintscolumnwidth}{0.6ex}}}%
  \hspace{\separatorcolumnwidth}%
  \parbox[m]{\maincolumnwidth}{\sectionstyle{#1}}\\[1ex]}

\begin{document}
\makecvtitle

\section{Work Experience}
\cventry[2,5mm]{05/2020--current}{Postdoc}{Max-Planck-Institute for Chemical Energy Conversion}{Mülheim a.d. Ruhr}{Working Group: Serena DeBeer}{
\begin{itemize}
\item Quantum chemical studies of geometric/electronic structure, and properties of enzymatic systems and model systems therof
\item Cooperative planning of theoretical and experimental studies
\item Coordination, exchange and discussion with international collaborators of different fields
\item Participation in intra- and interinstitutional symposiums and presentation of results
\end{itemize}
}

\cventry[2,5mm]{10/2014--04/2020}{Graduate Student}{Christian-Albrechts-Uni"-ver"-si"-tät}{Kiel}{Working Group: Felix Tuczek}{
\begin{itemize}
\item Synthesis and spectroscopic characterization of ligands and transition metal complexes.
\item Quantum chemical studies of geometric and electronic structure, calculation of spectra, comparison with experimental results.
\item Organization and execution of interdisciplinary cooperations with internal and external institutes.
\item Writing and publishing articles for scientific journals, solo and in collaboration.
\item Instruction of coworkers in conducting quantum chemical calculations. 
\item Organization and supervision of practical lab courses for students.
\end{itemize}
}
%\cventry[2,5mm]{06/2019}{Fortbildung: Basiszertifikat Projektmanagement}{Deutsche Gesellschaft für Projektmanagement e.\,V. (GPM)}{Kiel}{Mignon Krapf}{Techniken und Phasen des klassischen Projektmanagements, praktische Übungen, Teamleitung und Kommunikation.}
%\cventry[2,5mm]{02/2017}{Fortbildung: Betriebswirtschaftslehre für Chemiker: Grundlagen}{Gesellschaft Deutscher Chemiker e.\,V.}{Idstein}{Prof. Dr. Thorsten Daubenfeld}{Betriebswirtschaftslehre, Investitionsentscheidungen und betriebliches Rechnungswesen.}
%\cventry[2,5mm]{12/2016}{Fortbildung: Projekt- \& Zeitmanagement in der Wissenschaft}{Christian-Albrechts-Uni"-ver"-si"-tät}{Kiel}{Dr. Simon Golin}{Themenauswahl, Problembewältigung, Kooperation und Priorisierung.}
%\cventry[2,5mm]{11/2016}{Fortbildung: Projektmanagement \& Leadership}{Christian-Albrechts-Uni"-ver"-si"-tät}{Kiel}{Dr. Christina Schütte und Thomas Römer}{Anwendung klassischer Werkzeuge des Projektmanagements, Selbstorganisation, Delegation, Team-Motivation und Konfliktmanagement.}
%\cventry[2,5mm]{10/2015}{Fortbildung: Negotiation Skills}{Christian-Albrechts-Uni"-ver"-si"-tät}{Kiel}{Dr. Michael Jäger}{Konflikte und Vertrauen in Verhandlungen, Vorbereitung und Techniken der Verhandlungsführung, praktische Übungen. Kurssprache: Englisch.}
%\cventry{11/2008}{\href{https://raspberrypi.7700gg1rr8bnmkbx.myfritz.net/index.php/s/NRiGNGciW5Lgy5B}{Fortbildung: Human Resource Management}}{IHK Wirtschaftsakademie Schles"-wig-Hol"-stein}{Elmshorn}{Kursleitung: Udo Keller}{Inhalte: Managementmodelle, Führungskomponenten, Teambildung.}

\section{Education}
\cventry[2,5mm]{10/2014--04/2020}{Dissertation (Dr. rer. nat.): Chemistry}{Christian-Albrechts-Universität}{Kiel}{Supervisor: Felix Tuczek, Title: Quantum Chemical Investigation of Functional Molecules}{Grade: \textit{Magna cum laude}}
\cventry[2,5mm]{10/2012--09/2014}{Master of Science (M.Sc.): Chemistry}{Christian-Albrechts-Universität}{Kiel}{Focus: Inorganic and Quantum Chemistry}
{Grade: 1.6}
\cventry[2,5mm]{10/2009--09/2012}{Bachelor of Science (B.Sc.): Chemistry}{Christian-Albrechts-Uni"-versi"-tät}{Kiel}{Focus: Inorganic Chemistry}
{Grade: 1.8}
\cventry[2.5mm]{06/2009}{Abitur}{Hansa Gymnasium}{Hamburg}{}{Grade: 1.6}

%\newpage

%\section{Schulbildung}
%\cventry[2,5mm]{1999--2008}{Allgemeine Hochschulreife}{Max-Planck-Schule}{Kiel}{Abschlussnote: 1,3}{Empfehlung für die deutsche Studienstiftung als Jahrgangsbester. Teilnahme: Deutsche Schülerakademie 2007.}
%\cventry[2,5mm]{1995--1999}{Grundschule}{Jahnschule}{Kiel}{}{}

%\newpage

\section{Languages and Software Skills}
\cvitem{German}{Native}

\cvitem{English}{Fluent}
\cvitem{French}{Basic}
\cvitem{Elvish}{Basic}

\cvitem{Computational Chemistry}{ORCA, Gaussian, Turbomole, MOPAC, MRCC, Molpro, Psi4, Molcas, Amber}
\cvitem{Programming}{Rust, Python, git, bash}
\cvitem{Office}{\LaTeX, LibreOffice, Microsoft Office}

\newpage

%\cvitem{Grafik}{GIMP, CorelDraw, ChemDraw}
%\cvitem{Daten}{TopSpin, OriginPro, MestReNova}

\section{Trainings and Additional Experiences}
\cventry[2,5mm]{01/2019}{Training: Teamwork \& Leadership in academia}{Christian-Albrechts-Uni"-ver"-si"-tät}{Kiel}{Dr. Jaqcueline von Saldern}{}
\cventry[2,5mm]{12/2016}{Training: Project- \& Time Management in Science}{Christian-Albrechts-Uni"-ver"-si"-tät}{Kiel}{Dr. Simon Golin}{}
\cventry[2.5mm]{09/2016--04/2018}{Leading of local church group}{Freie evangelische Gemeinde}{Kiel}{Germany}{}

\section{Conference Contributions}
\cventry[2.5mm]{09/2018}{ORCA User Meeting}{Max-Planck-Institut für Kohlenforschung}{Mülheim a.d. Ruhr}{Germany}{Poster}
\cventry[2,5mm]{09/2017}{Norddeutsches Doktorandenkolloquium}{Christian-Albrechts-Universität}{Kiel}{Germany}{Presentation}
\cventry[2,5mm]{08/2017}{11th Triennial Congress of the World Association of Theoretical and Computational Chemists}{}{Munich}{Germany}{Poster}
\cventry[2,5mm]{06/2017}{Gordon Research Conference + Seminar: Artificial Molecular Switches and Motors}{Holderness School}{Holderness, NH}{USA}{Poster, Full travel stipend}
\cventry[2,5mm]{09/2015}{Summer School: Methods in Molecular Energy Research -- Theory and Spectroscopy}{Max-Planck-Institut für Chemische Energiekonversion}{Gelsenkirchen}{Germany}{Poster}
\cventry[2,5mm]{12/2014}{SFB 677 Winter Meeting}{Christian-Albrechts-Universität}{Kiel}{Germany}{Presentation}


\section{Publications}
\cvitem[2,5mm]{03/2020}{\textbf{B. M. Flöser}, Y. Guo, C. Riplinger, F. Tuczek, F. Neese,\
\grqq Detailed Pair Natural Orbital–based Coupled Cluster Studies of Spin Crossover Energetics\grqq,
\textit{J. Chem. Theory Comput.} \textbf{2020}, \textit{16}, 2224-2235. DOI:~\href{https://doi.org/10.1021/acs.jctc.9b01109}{10.1021/acs.jctc.9b01109}}
	
\cvitem[2,5mm]{05/2019}{T. R. Rusch, A. Schlimm, N. Krekiehn, \textbf{B. M. Flöser}, F. Röhricht, M. Hammerich, I. Lautenschläger, T. Strunskus, R. Herges, F. Tuczek, O. Magnussen,
\grqq Ordered Adlayers of a Combined Lateral Switch and Rotor\grqq,
\textit{J. Phys. Chem. C} \textbf{2019}, \textit{123}, 13720-13730. DOI:~\href{https://www.doi.org/10.1021/acs.jpcc.9b02469}{10.1021/acs.jpcc.9b02469}}

\cvitem[2,5mm]{04/2019}{B. Herzigkeit, R. Jurgeleit, \textbf{B. M. Flöser}, N. E. Meißner, T. A. Engesser, C. Näther, F. Tuczek
\grqq "Employing linear tridentate ligands with pyrazole endgroups in catalytic tyrosinase model chemistry: Does hemilability matter?\grqq,
\textit{Eur. J. Inorg. Chem.} \textbf{2019}, 2258-2266.                                                       DOI:~\href{https://www.doi.org/10.1002/ejic.201900242}{10.1002/ejic.201900242}}

\cvitem[2,5mm]{12/2018}{B. Herzigkeit, \textbf{B. M. Flöser}, N. E. Meißner, T. A. Engesser, F. Tuczek
\grqq Click. Coordinate. Catalyze. Using CuAAC Click Ligands in Small-Molecule Model Chemistry of Tyrosinase\grqq,
\textit{ChemCatChem} \textbf{2018}, \textit{10}, 5402-5405.                                                       DOI:~\href{https://www.doi.org/10.1002/cctc.201801606}{10.1002/cctc.201801606}}

\cvitem[2,5mm]{07/2018}{A. Schlimm, N. Stucke, \textbf{B. M. Flöser}, T. Rusch, J. Krahmer, C. Näther, T. Strunskus, O. M. Magnussen, F. Tuczek,
\grqq Influence of a Metallic Substrate on the Small Molecule Activation Mediated by a Surface Adsorbed Complex\grqq,
\textit{Chem. Eur. J.} \textbf{2018}, \textit{24}, 1-14.                                                       DOI:~\href{https://www.doi.org/10.1002/chem.201800911}{10.1002/chem.201800911}}

\cvitem[2,5mm]{04/2018}{B. Herzigkeit, \textbf{B. M. Flöser}, T. A. Engesser, C. Näther, F. Tuczek,
\grqq Tyrosinase model systems supported by pyrazolylmethylpyridine ligands: electronic and steric factors influencing the catalytic activity and impact of complex equilibria in solution\grqq,
\textit{Eur. J. Inorg. Chem.} \textbf{2018}, \textit{26}, 3058-3069.
DOI:~\href{https://www.doi.org/10.1002/ejic.201800319}{10.1002/ejic.201800319}}

\cvitem[2,5mm]{03/2018}{S. Rohlf, M. Gruber, \textbf{B. Flöser}, J. Grunwald, S. Jarausch, F. Diekmann, M. Kalläne, T. Jasper-Tönnies, A. Buchholz, W. Plass, R. Berndt, F. Tuczek, K. Rossnagel,
\grqq Light-Induced Spin Crossover in an Fe(II) Low-Spin Complex Enabled by Surface Adsorption\grqq,
\textit{J. Phys. Chem. Lett.} \textbf{2018}, \textit{9}, 1491-1496.
DOI:~\href{https://www.doi.org/10.1021/acs.jpclett.8b00338}{10.1021/acs.jpclett.8b00338}}

\cvitem[2,5mm]{03/2018}{N. Stucke, \textbf{B. M. Flöser}, T. Weyrich, F. Tuczek,
\grqq Nitrogen Fixation Catalyzed by Transition Metal Complexes: Recent Developments\grqq,
\textit{Eur. J. Inorg. Chem.} \textbf{2018}, 1337-1355.
DOI:~\href{https://www.doi.org/10.1002/ejic.201701326}{10.1002/ejic.201701326}}

\cvitem[2,5mm]{02/2018}{H. Brandenburg, J. Krahmer, K. Fischer, B. Schwager, \textbf{B. Flöser}, C. Näther, F. Tuczek,
\grqq Coordination-Induced Spin State Switching with Nickel(II) salpn complexes: electronic vs. steric effects and influence of intermolecular interactions\grqq,
\textit{Eur. J. Inorg. Chem.} \textbf{2018}, \textit{5}, 576-585.
DOI:~\href{https://www.doi.org/10.1002/ejic.201701281}{10.1002/ejic.201701281}}

\cvitem[2,5mm]{08/2017}{\textbf{B. M. Flöser}, F. Tuczek,
\grqq Synthetic nitrogen fixation with mononuclear molybdenum complexes: electronic-structural and mechanistic insights from DFT\grqq,
\textit{Coord. Chem. Rev.} \textbf{2017}, \textit{345}, 263-2.
DOI:~\href{https://www.doi.org/10.1016/j.ccr.2016.11.003}{10.1016/j.ccr.2016.11.003}}

\cvitem[2,5mm]{08/2016}{S. Hinrichsen, A.-C. Schnoor, K. Grund, \textbf{B. Flöser}, A. Schlimm, C. Näther, J. Krahmer, F. Tuczek,
\grqq Molybdenum dinitrogen complexes facially coordinated by linear tridentate PEP ligands (E = N or P): Impact of the central E donor in trans-position to N$_2$\grqq,
\textit{Dalton Trans.} \textbf{2016}, \textit{45}, 14801-14813.
DOI:~\href{https://www.doi.org/10.1039/C6DT02316A}{10.1039/C6DT02316A}}
\end{document}